### 2017-01-08 MSSM/MSSM.tex
Some more uncertainty work

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}
\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 6.2\% for
data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
applied to all processes for which the normalisation is estimated 
using \ac{MC} samples.
\subsubsection*{Identification, isolation and trigger efficiencies}
The uncertainty on electron and muon identification, isolation, and
trigger efficiency amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
isolation uncertainty amounts to 6\% in the \etau and \mutau channels
and 12\% in the \tautau channel, with an additional 7\% uncertainty
on the tau trigger efficiency added in quadrature for that channel \cite{CMS-PAS-HIG-16-037}. This
uncertainty is split between a part that is correlated between the channels, 
a 5\% (10\%) uncertainty in the \etau and \mutau (\tautau) channels. The uncorrelated 
part amounts to 3\% (9.2\%) for the \etau and \mutau (\tautau) channels.
The uncertainties on lepton/hadronic tau identificiation, isolation and 
trigger efficiency are applied to all processes for which the normalisation
is estimated using \ac{MC} samples.
\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
The uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate
is 20\% \cite{cms-tau-2015}. This uncertainty is applied
to those backgrounds where the normalisation is estimated from \ac{MC} and
where the hadronic taus are mimicked by jets, that is the \Zellell background
with a jet faking a hadronic tau, the \Wjets background in the fully hadronic
channel, and the \ttbar background with a jet faking a hadronic tau. 
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
The $\Pe\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 10-30\%,
depending on the anti-electron discriminator used \cite{cms-tau-2015}. This uncertainty is 
applied to the \Zellell background with the hadronic tau faked by an electron.
The $\Pgm\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 20-30\%, depending
on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
background with the hadronic tau faked by a muon.
\subsubsection*{Jet energy scale uncertainty}
The uncertainties on the jet-energy corrections are applied
by shifting the jet energy up and down by the \pT~ and $\eta$ dependendent
uncertainty, and evaluating the the change in process normalisation in
each category. Where the change in normalisation is non-negligible the
uncertainty is applied. It ranges from 1--10\% depending on process and category.
\subsubsection*{B-tag scale factors}
Uncertainties on the b-tagging efficiency and light jet mis-tagging
rates are given as a function of jet \pT~ and $\eta$ for the 
medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
The b-tagging scale factors are are varied within these uncertainties
and the overall change in normalisation for each process in each category is
evaluated. If the change in normalisation is non-negligible this
uncertainty is applied. The uncertainty varies from 1--5\%.
\subsubsection*{\MET resolution and response}
\subsubsection*{Background normalisation}
\subsubsection*{Theory uncertainties}

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
\subsubsection*{Electron energy scale}
\subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
\subsubsection*{Top quark \pT~ reweighting}
\subsubsection*{Drell-Yan shape reweighting}
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}

\section{Signal extraction}
\label{sec:mssm_signalextraction}

@@

>>>>

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}
\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 6.2\% for
data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
applied to all processes for which the normalisation is estimated 
using \ac{MC} samples.
\subsubsection*{Identification, isolation and trigger efficiencies}
The uncertainty on electron and muon identification, isolation, and
trigger efficiency amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
isolation uncertainty amounts to 6\% in the \etau and \mutau channels
and 12\% in the \tautau channel, with an additional 7\% uncertainty
on the tau trigger efficiency added in quadrature for that channel \cite{CMS-PAS-HIG-16-037}. This
uncertainty is split between a part that is correlated between the channels, 
a 5\% (10\%) uncertainty in the \etau and \mutau (\tautau) channels. The uncorrelated 
part amounts to 3\% (9.2\%) for the \etau and \mutau (\tautau) channels.
The uncertainties on lepton/hadronic tau identificiation, isolation and 
trigger efficiency are applied to all processes for which the normalisation
is estimated using \ac{MC} samples.
\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
The uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate
is 20\% \cite{cms-tau-2015}. This uncertainty is applied
to those backgrounds where the normalisation is estimated from \ac{MC} and
where the hadronic taus are mimicked by jets, that is the \Zellell background
with a jet faking a hadronic tau, the \Wjets background in the fully hadronic
channel, and the \ttbar background with a jet faking a hadronic tau. 
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
The $\Pe\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 10-30\%,
depending on the anti-electron discriminator used \cite{cms-tau-2015}. This uncertainty is 
applied to the \Zellell background with the hadronic tau faked by an electron.
The $\Pgm\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 20-30\%, depending
on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
background with the hadronic tau faked by a muon.
\subsubsection*{Jet energy scale uncertainty}
The uncertainties on the jet-energy corrections are applied
by shifting the jet energy up and down by the \pT~ and $\eta$ dependendent
uncertainty, and evaluating the the change in process normalisation in
each category. Where the change in normalisation is non-negligible the
uncertainty is applied. It ranges from 1--10\% depending on process and category.
\subsubsection*{B-tag scale factors}
Uncertainties on the b-tagging efficiency and light jet mis-tagging
rates are given as a function of jet \pT~ and $\eta$ for the 
medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
The b-tagging scale factors are are varied within these uncertainties
and the overall change in normalisation for each process in each category is
evaluated. If the change in normalisation is non-negligible this
uncertainty is applied. The uncertainty varies from 1--5\%.
\subsubsection*{\MET resolution and response}
Uncertainties on \MET resolution and response are estimated
by varying the recoil correction paramters within their
uncertainty and evaluating the effect on process
normalisations. The uncertainty amounts to around 2\%
\subsubsection*{Background normalisation}
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \Ztautau: As the \Zmm control region is included in the simultaneous
fit with the signal region to correct the \Ztautau normalisation
the Drell-Yan cross section is not applied as an uncertainty. A 3\% (5\%)
extrapolation uncertainty from \Zmm $\rightarrow$ \Ztautau is applied in 
the no b-tag (b-tag) category \cite{CMS-PAS-HIG-16-037}.
\item \Zellell: The uncertainty on the Drell-Yan cross-section
amounts to 4\% \cite{CMS-PAS-HIG-16-037}.
\item \ttbar: The uncertainty on the \ttbar cross-section amounts
to 6\% \cite{CMS-PAS-HIG-16-037}.
\item di-boson and single-top: The uncertainty on the di-boson and
single-top production cross-sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.
\item \Wjets:
\item QCD:
\end{itemize}
\subsubsection*{Theory uncertainties}

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}. As the 
shape of the total transverse mass distribution depends on the energy of the $\Pgt_{h}$
it is applied as a shape uncertainty. It is applied to the signal samples and to
backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels:
\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
hadronic taus.
\subsubsection*{Electron energy scale}
The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This affects
the shape of the total transverse mass distribution, and this uncertainty is applied to the
signals and to the \Ztautau background.
\subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
An additional $\Pgt_{h}$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\text{TeV}}$
is applied to account for the extrapolation from the tau ID efficiency
measurement, which uses mostly taus close to the Z peak, to taus with higher \pT s. This
uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels
\subsubsection*{Top quark \pT~ reweighting}
To account for the uncertainty in the derivation of the top-quark \pT~ reweighting, a shape
uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
of the correction, ie the difference between applying the correction twice and not applying the correction at all.
\subsubsection*{Drell-Yan shape reweighting}
An uncertainty on the Drell-Yan shape reweighting based on \Zmm events
is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
On the \Wjets background in the \etau and \mutau channels a shape 
uncertainty of $\frac{-20\% \times p_{\text{T}}}{\text{GeV}}$ is 
applied. This uncertainty is derived from variations in the data/MC ratio
for the jet$\rightarrow\Pgt_{h}$ fake rate as a function of jet \pT~ in 
\Wjets events \cite{CMS-PAS-HIG-16-037}.

\section{Signal extraction}
\label{sec:mssm_signalextraction}
The total transverse mass \mTtot~ is used as discriminating variable in this analysis.
All bins of the distribution are used to perform a shape analysis. The statistical
methods, including the incorporation of nuisance parameters in the fit, were already
described in section \ref{sec:hhh_results_extraction}. Some additional
methods are used for this analysis, and they will be discussed in this section.

@@

\subsection{MSSMvsSM hypothesis testing}
\label{sec:mssm_sigext_mssmvssm}
